---
title: "R Notebook"
output: html_notebook
---


```{r}
source("global.R")
source("shinyCache2.R")
#load("callmat.RData")
#callgr <- callmat
datadir <- "../data.chm"
ids <- c("16c58fbcc5633564b10ebe8f78d87883",
		"40c68f29b6d7cb2358f31a7073250406",
		"43a13d07730deb934e9fc01e3b3cd26f",
		"8dcad8fe04f4ebc0ad3254ab4420cdc8",
		"acd889cc16741fb0fba62faa4f7005f3",
		"b1112f1c3cbd28c464f58fc5c5c02f9b",
		"9d134f160ac68c0445002fbb78db4a5e")
callmat <- .LoadCallMatrixForIds(
	datadir=datadir,
	metadata=LoadCachedMetadata(datadir),
	ids=c("00000000000000000000000000000001", ids),
	ignore.interchromosomal=TRUE, mineventsize=51, maxeventsize=NULL,
	maxgap=200,
	sizemargin=0.25,
	ignore.strand=TRUE,
	grtransform=.primaryHumanOnly,
	grtransformName="test"
)

datadir <- "../data.na12878"
ids <- c(
		#"2f4d15f5f6e428fb91e12dac971571b9", #bcftools
		#"5cdeeb9fd824f642f0ebee04627adf6e", gridss 1.2.1
		"6ae03359fcf0a39aa236a0aaea7ea915",
		"8aaf2886ffe782e666661d6b890b330a",
		"80dd0c2aa34964f330702ee3d0bfa53f",
		"1139a1e6ef2d598098fe5c2ff609052a",
		"26511afa5055a939fdf99a2ac24938cc",
		"a6cbc4fc76337d871ef899d51fbae0d9",
		"b6aeda0d81ff8c839e381b57898dc3d8",
		#"e77293fb821458c3fd04c58ea88b7b16", #gasv
		#"ee44a2b21004af249f115bb5d9508ceb", gridss 1.3.0
		#"f75b305c5579449e347c1b87832e65d8", #gasv
		"f849b9493f2dd5dc20b6b7e49e1c89d7",
		"fa5f9a52d3b67a206cb6e581053a9269")
callgr <- .LoadCallMatrixForIds(
	datadir=datadir,
	metadata=LoadCachedMetadata(datadir),
	ids=c(
		"00000000000000000000000000000000",
		"00000000000000000000000000000001",
		"00000000000000000000000000000002",
		"00000000000000000000000000000003",
		ids),
	ignore.interchromosomal=TRUE, mineventsize=51, maxeventsize=NULL,
	maxgap=200,
	sizemargin=0.25,
	ignore.strand=TRUE,
	grtransform=.primaryHumanOnly,
	grtransformName="test"
)
# callgr <- callgr[simpleEventType(callgr) == "DEL"]

source("sv_benchmark.R")
callgr$simpleEvent <- simpleEventType(callgr)
callgr <- callgr[!is.na(callgr$svLen) & abs(callgr$svLen) < 50000]
names(callgr) <- NULL # could be duplicates
callgr$QUAL[is.na(callgr$QUAL)] <- 1

```

PCA plot of calls made

```{r}

calldf <- mcols(callmat)
calldf <- calldf[,(1+which("Id" == names(calldf))):length(names(calldf))]
callm <- as.matrix(calldf)

```

We now want to rescale ouur QUALs so they are comparable.
since we make no assumptions on the shape of the QUAL, the transform
can be arbitrary, we only require it to be monotonic

Lets try CDF of precision

Rolling window of precision
```{r}
require(tidyverse)
require(zoo)
require(ggplot2)
for (id in ids) {
	print(data.frame(qual=callgr[callgr$Id==id]$QUAL, tp=callgr[callgr$Id==id]$Id00000000000000000000000000000001 != -1) %>%
		arrange(qual) %>%
		mutate(
			windowprec100=rollmean(tp, k=100, fill=FALSE, align="right"),
			windowprec250=rollmean(tp, k=250, fill=FALSE, align="right"),
			windowprec1000=rollmean(tp, k=1000, fill=FALSE, align="right")
			) %>%
		ggplot(aes(x=qual)) +
		geom_point(aes(y=windowprec100), colour="red") +
		geom_point(aes(y=windowprec250), colour="green") +
		geom_point(aes(y=windowprec1000), colour="blue"))
}
```

Leon suggested that a lowess fit was more appropriate as it weights nearby points according to their distance in QUAL space

Lachlan suggested smooth.spline to fit the QUAL-precision curve

```{r}
for (id in ids) {
	ssz <- smooth.spline(x=callgr[callgr$Id==id]$QUAL, y=as.numeric(callgr[callgr$Id==id]$Id00000000000000000000000000000001 != -1), spar=0.5, tol=0.5)
	plot(ssz)
}
```

Log transform

```{r}
for (id in ids) {
	df <- data.frame(
			logq=log10(callgr[callgr$Id==id]$QUAL + 2),
			tp=callgr[callgr$Id==id]$Id00000000000000000000000000000001 != -1) %>%
		group_by(logq) %>%
		summarise(
			prec=sum(tp)/n(),
			w=n()
			)
	ssz <- smooth.spline(x=df$logq, y=df$prec, w=df$w, tol=1e-3)
	plot(ssz)
}
```

Plot QUAL bins

```{r}
require(binom)
for (id in ids) {
	df <- data.frame(
			q=callgr[callgr$Id==id]$QUAL,
			logq=log10(callgr[callgr$Id==id]$QUAL + 1),
			tp=callgr[callgr$Id==id]$Id00000000000000000000000000000001 != -1) %>%
		mutate(
			qbin=cut(q, breaks=(0:100)/100*max(q), labels=(0:99)/100*max(q)),
			logqbin=cut(logq, breaks=(0:100)/100*max(logq), labels=(0:99)/100*max(logq))) %>%
		group_by(qbin) %>%
		summarise(
			qmean=mean(q),
			logqmean=mean(logq),
			n=n(),
			prec=sum(tp)/n(),
			prec_lower=binom.confint(sum(tp), n(), 0.95, methods="exact")$lower,
			prec_upper=binom.confint(sum(tp), n(), 0.95, methods="exact")$upper)
	myplot <- ggplot(df) +
		aes(x=qmean,
			ymin=prec_lower,
			y=prec,
			ymax=prec_upper) +
		geom_errorbar() +
		geom_point(colour="blue")
		#stat_smooth(method="gam", method.args=list(family=binomial()))
	print(myplot)
}
```

```{r}
require(binom)
for (id in ids) {
	df <- data.frame(
			q=callgr[callgr$Id==id]$QUAL,
			logq=log10(callgr[callgr$Id==id]$QUAL + 1),
			tp=callgr[callgr$Id==id]$Id00000000000000000000000000000001 != -1) %>%
		mutate(
			qbin=cut(q, breaks=(0:100)/100*max(q), labels=(0:99)/100*max(q)),
			logqbin=cut(logq, breaks=(0:100)/100*max(logq), labels=(0:99)/100*max(logq))) %>%
		group_by(logqbin) %>%
		summarise(
			qmean=mean(q),
			logqmean=mean(logq),
			n=n(),
			prec=sum(tp)/n(),
			prec_lower=binom.confint(sum(tp), n(), 0.95, methods="exact")$lower,
			prec_upper=binom.confint(sum(tp), n(), 0.95, methods="exact")$upper)
	myplot <- ggplot(df) +
		aes(x=logqmean,
			ymin=prec_lower,
			y=prec,
			ymax=prec_upper) +
		geom_errorbar(aes(alpha=pmin(1, n/20))) +
		geom_point(colour="blue") #aes(size=log10(n)), 
		#stat_smooth(method="gam", method.args=list(family=binomial()))
	print(myplot)
}
```

```{r}
require(binom)
df <- data.frame(
		id=callgr$Id,
		q=callgr$QUAL,
		logq=log10(callgr$QUAL + 1),
		tp=callgr$Id00000000000000000000000000000001 != -1) %>%
	group_by(id) %>%
	mutate(
		qbin=as.numeric(as.character(cut(q, breaks=(0:100)/100*max(q), labels=(0:99)/100*max(q)))),
		logqbin=as.numeric(as.character(cut(logq, breaks=(0:100)/100*max(logq), labels=(0:99)/100*max(logq))))) %>%
	group_by(id, logqbin) %>%
	summarise(
		qmean=mean(q),
		logqmean=mean(logq),
		n=n(),
		prec=sum(tp)/n(),
		prec_lower=binom.confint(sum(tp), n(), 0.95, methods="exact")$lower,
		prec_upper=binom.confint(sum(tp), n(), 0.95, methods="exact")$upper)
ggplot(df) +
	aes(x=logqmean,
		ymin=prec_lower,
		y=prec,
		ymax=prec_upper) +
	coord_cartesian(ylim=c(0,1)) + 
	geom_errorbar(aes(alpha=pmin(1, n/20))) +
	geom_point(colour="blue") + #aes(size=log10(n)), 
	facet_wrap(~ id, scales="free")
	#stat_smooth(method="gam", method.args=list(family=binomial()))
```

Trying a stacked plot w/ a histogram:

```{r}
require(cowplot)

test_df <- 
    df %>%
    filter(id == "1139a1e6ef2d598098fe5c2ff609052a")

ci_plot <-
    test_df %>%
    ggplot() +
	aes(x=logqmean,
		ymin=prec_lower,
		y=prec,
		ymax=prec_upper) +
	coord_cartesian(ylim=c(0,1)) + 
	geom_errorbar(aes(alpha = n > 10), color = "grey70") +
    scale_alpha_manual(values = c(0, 1)) +
	geom_point(aes(color = n > 10)) +
    scale_color_manual(values = c("grey70", "#396AB1")) +
    cowplot::theme_cowplot() +
    cowplot::background_grid(major = "xy", minor = "none") +
    theme(
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(1, 1, -0.2, 1), "lines"))

hist_plot <-
    test_df %>%
    ggplot() +
    aes(x = logqmean, y = -log10(n)) +
    geom_col(
        # Width manually in here?
    ) +
    # cowplot::theme_nothing() +
    cowplot::background_grid(major = "xy", minor = "none") +
    theme(
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        plot.margin = unit(c(0, 1, 1, 1), "lines")) +
    scale_y_continuous(
        expand = c(0,0)
        # Doesn't appear to work yet
        # breaks = function(y_limits) {1:(y_limits[2] + 1)}
        )
```

```{r}
ci_plot
```

```{r}
hist_plot
```

```{r}
hist_grob <-
    ggplotGrob(hist_plot)

ci_grob <-
    ggplotGrob(ci_plot)
```

```{r}
require(gtable)
require(gridExtra)

g <- gridExtra::rbind.gtable(
    ci_grob, hist_grob, 
    size = "first")

grid.newpage()
grid.draw(g)
```

Try `grid.arrange` -- note that it doesn't handle the shared
axes properly:

```{r}
g1 <- grid.arrange(
    ci_grob, hist_grob, ncol = 1)

grid.newpage()
grid.draw(g1)
```

Rearrange heights above via the approach at ```http://felixfan.github.io/stacking-plots-same-x/#different-heights-same-widths```

```{r}
ci_built <-
    ggplot_build(ci_plot)

hist_built <-
    ggplot_build(hist_plot)

layout_indices <- grep("panel", g$layout$name)

panels <- g$layout$t[layout_indices]

g$heights[panels] <- g$heights[panels] * c(3,1)

grid.newpage()
grid.draw(g)
```

Try raw smoothing
```{r}
for (id in ids) {
	df <- data.frame(
			q=callgr[callgr$Id==id]$QUAL,
			logq=log10(callgr[callgr$Id==id]$QUAL + 1),
			tp=as.numeric(callgr[callgr$Id==id]$Id00000000000000000000000000000001 != -1))
	myplot <- ggplot(df) +
		aes(x=q, y=tp) +
		geom_smooth() +
		coord_cartesian(ylim=c(0,1))
	print(myplot)
}
```



Precision/recall plot

```{r}

callgr$caller_hits_ex_truth <- rowSums(as.matrix(as.data.frame(mcols(callgr)[,str_detect(names(mcols(callgr)), "Id[a-f0-9]+") &
		!(names(mcols(callgr)) %in% c(
			"Id00000000000000000000000000000000",
			"Id00000000000000000000000000000001",
			"Id00000000000000000000000000000002",
			"Id00000000000000000000000000000003"))])) != -1)

rocby <- function(callgr, ..., rocSlicePoints=100, truthid="00000000000000000000000000000001") {
	eventCount <- sum(callgr$Id == truthid)
	groupingCols <- quos(...)
	callgr$truth <- mcols(callgr)[[paste0("Id",truthid)]]
	as.data.frame(callgr) %>%
		dplyr::select(Id, CallSet, !!!groupingCols, QUAL, truth) %>%
		group_by(Id, CallSet, !!!groupingCols, QUAL) %>%
		summarise(
			fp=sum(truth == -1),
			tp=sum(truth != -1)) %>%
		group_by(Id, CallSet, !!!groupingCols) %>%
		arrange(desc(QUAL)) %>%
		mutate(
			fp=cumsum(fp),
			tp=cumsum(tp)) %>%
		# each QUAL score is a point on the ROC plott
		group_by(Id, CallSet, !!!groupingCols, QUAL) %>%
		summarise(tp=max(tp), fp=max(fp)) %>%
		# QUAL scores with the same number of tp calls can be merged on the ROC plot
		group_by(Id, CallSet, !!!groupingCols, tp) %>%
		summarise(fp=max(fp), QUAL=min(QUAL)) %>%
		# subsample along tp and tp+fp axis
		group_by(Id, CallSet, !!!groupingCols) %>%
		dplyr::slice(unique(c(
			1,
			findInterval(seq(0, max(tp), max(tp)/rocSlicePoints), tp),
			findInterval(seq(0, max(tp + fp), max(tp + fp)/rocSlicePoints), tp + fp),
			n()
		))) %>%
		ungroup() %>%
		mutate(
			fn=eventCount-tp,
			precision=tp / (tp + fp),
			fdr=1-precision,
			sens=tp/eventCount)
}

```

By Shared hits & event type

```{r}

rocbySharedHits <- rocby(callgr, simpleEvent, caller_hits_ex_truth)

ggplot(rocbySharedHits %>% filter(Id != "00000000000000000000000000000001")) +
	aes(y=precision, x=tp, colour=Id, linetype=CallSet) +
	geom_line() +
	facet_grid(simpleEvent ~ caller_hits_ex_truth)
	labs(title="Precision-Recall by number of callers sharing call")

```

By event type

```{r}

rocbyeventType <- rocby(callgr, simpleEvent)

ggplot(rocbySharedHits %>% filter(Id != "00000000000000000000000000000001")) +
	aes(y=precision, x=tp, colour=Id, linetype=CallSet) +
	geom_line() +
	facet_wrap(~ simpleEvent)
	labs(title="Precision-Recall by event type")

```

By shared hits

```{r}
ggplot(rocby(callgr, caller_hits_ex_truth, truthid="00000000000000000000000000000003") %>% filter(!(Id %in% c("00000000000000000000000000000000", "00000000000000000000000000000001", "00000000000000000000000000000002", "00000000000000000000000000000003")))) +
	aes(y=precision, x=tp, colour=Id, linetype=CallSet) +
	geom_line() +
	facet_wrap( ~ caller_hits_ex_truth, scale="free") + 
	scale_colour_brewer(palette="Set1")
	labs(title="Precision-Recall by number of callers sharing call")

```


Overall ROCs by truth set

```{r}
rocfull <- rocby(callgr, truthid="00000000000000000000000000000000") %>% mutate(truth="00000000000000000000000000000000") %>% rbind(
	rocby(callgr, truthid="00000000000000000000000000000001") %>% mutate(truth="00000000000000000000000000000001")) %>% rbind(
	rocby(callgr, truthid="00000000000000000000000000000002") %>% mutate(truth="00000000000000000000000000000002")) %>% rbind(
	rocby(callgr, truthid="00000000000000000000000000000003") %>% mutate(truth="00000000000000000000000000000003"))

ggplot(rocfull %>% filter(!(Id %in% c("00000000000000000000000000000000", "00000000000000000000000000000001", "00000000000000000000000000000002", "00000000000000000000000000000003")))) +
	aes(y=precision, x=tp, colour=Id, linetype=CallSet) +
	geom_line() +
	facet_wrap( ~ truth, scale="free") + 
	scale_colour_brewer(palette="Set1")
	labs(title="Precision-Recall by number of callers sharing call")

```


Missed by GRIDSS
```{r}


callgr[
	callgr$Idb1112f1c3cbd28c464f58fc5c5c02f9b == -1 &
	callgr$caller_hits_ex_truth > 0 &
	callgr$Id =="00000000000000000000000000000001"]

```

Unique by annotation

```{r}
truthvcf <- readVcf("../data.chm/00000000000000000000000000000001.vcf", "")
repeattruth <- info(truthvcf)$REPEAT_TYPE
names(repeattruth) <- names(rowRanges(truthvcf))
truthgr <- breakpointRanges(truthvcf, info_columns="REPEAT_TYPE")
truthgr$repeatAnn <- ifelse(is.na(truthgr$REPEAT_TYPE), "NotMasked", truthgr$REPEAT_TYPE)
callgr$repeatAnn <- ""
callgr$repeatAnn[callgr$Id =="00000000000000000000000000000001"] <- repeattruth[callgr$vcfId[callgr$Id =="00000000000000000000000000000001"]]
callgr$repeatAnn[callgr$Id =="00000000000000000000000000000001" & is.na(callgr$repeatAnn)] <- truthgr$repeatAnn[findOverlaps(
	callgr[callgr$Id =="00000000000000000000000000000001" & is.na(callgr$repeatAnn)],
	truthgr,
	type="equal", select="first")]
```

Common calls by repeat annotation

```{r}

ggplot(as.data.frame(callgr[callgr$Id =="00000000000000000000000000000001"])) +
	aes(fill=factor(caller_hits_ex_truth), x=repeatAnn) +
	geom_bar() + 
	theme(axis.text.x=element_text(angle=90,hjust=1)) +
	facet_wrap(simpleEvent ~ cut(abs(svLen), breaks=c(0, 50, 100, 1000, 100000), right=FALSE), scales = "free")

```






















